---
title: "Bayesian Modeling of Prosodic Features"
author: "Your Name"
date: "`r Sys.Date()`"
output: html_document
---

# ✅ **Setup**

```{r setup, message=FALSE, warning=FALSE}
library(tidyverse)
library(brms)
library(tidybayes)
library(bayesplot)
library(here)
library(knitr)

# Load the data
df <- read_csv("data/daic_prosodic_summary_60s.csv") %>%
  mutate(
    participant_id = factor(participant_id),
    window = factor(window)
  )
```

---

# 📌 **Bayesian Model: Pitch Variation**

This model assesses variability in pitch (`pitch_sd`) across participants.

```{r pitch_sd_model, cache=TRUE}
pitch_sd_model <- brm(
  pitch_sd ~ 1 + (1 | participant_id),
  data = df,
  family = gaussian(),
  chains = 4,
  iter = 4000,
  warmup = 1000,
  cores = parallel::detectCores(),
  control = list(adapt_delta = 0.95),
  seed = 123
)
```

---

# 📌 **Model Diagnostics**

Visual checks for convergence and stability.

```{r diagnostics}
plot(pitch_sd_model)
pp_check(pitch_sd_model)
```

---

# 📌 **Model Summary**

Model parameters and credible intervals.

```{r summary}
summary(pitch_sd_model)
```

---

# 📌 **Top Participants by Pitch Variation**

List participants with highest estimated pitch variability.

```{r random_effects_table}
ranef(pitch_sd_model)$participant_id %>%
  as.data.frame() %>%
  arrange(desc(Estimate.Intercept)) %>%
  head(10) %>%
  knitr::kable(
    digits = 3,
    caption = "Top 10 Participants by Pitch Variation (Random Effects)"
  )
```

---

# 📌 **Optional: Bayesian Model for Energy Variation**

Repeat similar modeling for energy variability if desired.

```{r energy_sd_model, eval=FALSE}
energy_sd_model <- brm(
  energy_sd ~ 1 + (1 | participant_id),
  data = df,
  family = gaussian(),
  chains = 4,
  iter = 4000,
  warmup = 1000,
  cores = parallel::detectCores(),
  control = list(adapt_delta = 0.95),
  seed = 123
)
```

---

# 📌 **Interpretation for Clinicians**

- **Higher pitch or energy variation** may suggest emotional instability or anxiety.
- **Lower pitch or energy variation** could suggest a flat affect or depressive mood.

These insights can guide clinical interpretations within your RAG system.